---
title: "Brand Preference"
output: github_document
author: "Gherardo Lattanzi"
---
#### Costumer Brand Preference ####
Hi Danielle, the following is the investigation on wether our customers prefers Acer or Sony. The following should not be unfamiliar with you, since the processes from analysing and cleaning the dataset are mainly the same we worked in RapidMiner. 

```{r}
CompleteResponses <- read.csv("../Desktop/UBIQUM/CompleteResponses.csv")
SurveyIncomplete <- read.csv("~/Desktop/UBIQUM/SurveyIncomplete.csv")

```

Those are the two libraries I have used to craft this presentation. 
```{r}
library(caret)
library(ggplot2)
```

# Data Cleaning Operations
```{r}
CompleteResponses$elevel <- as.integer(CompleteResponses$elevel)
CompleteResponses$car <- as.factor(CompleteResponses$car)
CompleteResponses$brand <- as.factor(CompleteResponses$brand)
CompleteResponses$zipcode <- as.factor(CompleteResponses$zipcode)
CompleteResponses$age <- as.numeric(CompleteResponses$age)


SurveyIncomplete$elevel <- as.integer(SurveyIncomplete$elevel)
SurveyIncomplete$car <- as.factor(SurveyIncomplete$car)
SurveyIncomplete$brand <- as.factor(SurveyIncomplete$brand)
SurveyIncomplete$zipcode <- as.factor(SurveyIncomplete$zipcode)
SurveyIncomplete$age <- as.numeric(SurveyIncomplete$age)
```

The following are graphical representations of the relationship between the attributes 
of our customers. 
# Brand Preference for Salary and Age
```{r}
library(ggplot2)
ggplot(CompleteResponses, aes(x=age, y=salary, col=brand)) +
  geom_point() +
  geom_smooth()

```

```{r echo=FALSE}
library(ggplot2)
ggplot(CompleteResponses, aes(x=age, fill=brand)) + geom_histogram(color="black", bins=10)

#With this graph we can easily see how the age and the salary identify macro differences in the
#average customer brand preferences.
```

Question 1: What is your yearly salary, not including bonuses?

```{r}
hist(CompleteResponses$salary, breaks = 100)
```

Question 2: What is your age?

```{r}
hist(CompleteResponses$age, breaks = 100)

```


Question 4: What is your car?


Where: 1 = BMW, 2 = Buick, 3 = Cadillac, 4 = Chevrolet, 5 = Chrysler, 6 = Dodge, 7 = Ford, 8 = Honda, 9 = Hyundai, 10 = Jeep, 11 = Kia, 12 = Lincoln, 13 = Mazda, 14 = Mercedes Benz, 15 = Mitsubishi, 16 = Nissan, 17 = Ram, 18 = Subaru, 19 = Toyota, 20 = None of the above


```{r}
ggplot(CompleteResponses, aes(x = car, fill = brand)) + geom_bar(colour = "black")

```


```{r}
ggplot(CompleteResponses, aes(x = credit, fill = brand)) + geom_histogram(colour = "black")

```



# Define an 75%/25% train/test split
```{r}
inTraining <- createDataPartition(CompleteResponses$brand, p = .75, list = FALSE)
training <- CompleteResponses[inTraining,]
testing <- CompleteResponses[-inTraining,]

```

# 10 fold cross validation

```{r}
fitControl <- trainControl(method = "repeatedcv", number = 10, repeats = 2)
```

# Random Forest Modelling
```{r echo=FALSE}
#M0D <- train(brand~., data = training, method = "rf", trControl=fitControl, tuneLength = 2, list = FALSE )

#varImp(M0D)
#train Random Forest Regression model with a tuneLenght = 2 
load("dataMOD.RData")
```

```{r}
PRED1 <- predict(M0D, testing)
summary(PRED1)
#SurveyIncomplete$brand <- PRED1
```

# Confusion Matrix 
```{r}
confusionMatrix(PRED1, testing$brand)
```

#######################################################################################
with other method
#######################################################################################

#### C5.0 Modelling ####
```{r echo=FALSE}
#MODC5 <- train(brand~., data = training, method = "C5.0", trControl=fitControl, tuneLength = 2, list = FALSE)
#print(MODC5)
#str(MODC5)

load("dataMOD5C.RData")

```
# Apply Model to SurveyIncomplete

```{r}
PRED2 <- predict(MODC5, SurveyIncomplete)

```

This is to compare the testing brand preference prediction and the actual value. 
```{r}
postResample <- postResample(PRED2, testing$brand) 

```

```{r}
varImp(MODC5)
```

```{r eval=FALSE, include=FALSE}
ConfusionM <- confusionMatrix(PRED2, testing$brand)
ConfusionM

```

```{r}
TotData <-rbind(SurveyIncomplete, CompleteResponses)

```

# Total Number of Acer and Sony Preferences Sampled
```{r}
#summary(TotData$brand)
#  0(Acer)    1(Sony)
#  8744         6154 


```


